Reproducibility of SNP calling in multiple sequencing runs from single tumors

### 2015-03-20 PAPER/paper_d1.tex

%A) What is the general field of study?
Glioblastoma multiforme (GBM) is the most common and deadly primary brain tumor, with a median survival of 13.9 months and a 5-year survival of ~5\% \cite{TCGA-GBM-13}. Prognosis for patients with this disease remains poor despite significant research investment, due to the difficulty of surgical resection and the limited number of effective chemoteraputics. Like all cancers, GBM is an evolutionary disease caused by mutations and other alterations to normal glial cell lines. However, following substantial research efforts dedicated to identifying all of the mutations in an individual patient's tumor to try and identify causal variants, few precise causal elationships have been identified. There are likely many related causes for this failure, including but not limited to genomic heterogeneity in tumors, \cite{ValentineD}, the view that "GBM growth is driven by a signaling network with functional redundancy that permits adaptation" \cite{TCGA-GBM-13}, and imperfect computational methods. 
%B) What is the specific question of the research?
In this paper, we are interested in the third. We used technical sequencing replicates from 55 GBM tumors to look at the reproducbility of the raw data using a standard computational pipeline. Assuming that those mutations that appear in each of the technical replicates are true positives, and all others are false positives (which in fact may or may not be true), we want to see what proportion of mutations recovered are ture positives, and whether or not the proportion is increased by SNP-calling methods designed to remove false positives.

>>>>

%A) What is the general field of study?
Glioblastoma multiforme (GBM) is the most common and deadly primary brain tumor, with a median survival of 13.9 months and a 5-year survival of ~5\% \cite{TCGA-GBM-13}. Prognosis for patients with this disease remains poor despite significant research investment, due to the difficulty of surgical resection and the limited number of effective chemoteraputics. Like all cancers, GBM is an evolutionary disease caused by mutations and other alterations to normal glial cell lines. However, following substantial research efforts dedicated to identifying all of the mutations in an individual patient's tumor to try and identify causal variants, few precise causal elationships have been identified. There are likely many related causes for this failure, including but not limited to genomic heterogeneity in tumors, \cite{ValentineD}, the view that "GBM growth is driven by a signaling network with functional redundancy that permits adaptation" \cite{TCGA-GBM-13}, and imperfect computational methods. 
%B) What is the specific question of the research?
In this paper, we are interested in the third. We used technical sequencing replicates from 55 GBM tumors to look at the reproducbility of the raw data using a standard computational pipeline. Assuming that those mutations that appear in each of the technical replicates are true positives, and all others are false positives (which in fact may or may not be true), we want to see what proportion of mutations recovered are true positives, and whether or not the proportion is increased by SNP-calling methods designed to remove false positives.
